\section{Discussion}

The present results do not establish a global compression shadow. They
establish something weaker and more bounded.

First, a local replay-stable bounded homeward-alignment compression signature
exists for the admitted return-cell one-step information transport. Under the
conservative target-home proxy, mean distance to receipt home decreased from
2.75 to 0.0 and support radius decreased from 5 to 0, while support size and
support entropy remained invariant. The transport therefore does not compress
by shrinking support. It compresses by aligning support homeward.

Second, the six-nine return-home ledger appears to belong to a different
surface class. The six-nine rowsets expose a receipt-strong surface anatomy
rather than a directed transport history. Their dominant parsed slotset is the
expanded surface with gap class, represented by the slotset
$\{3,6,9,11,12\}$.

These observations motivate a provisional distinction between two kinds of
compression-relevant surfaces:

\begin{itemize}
  \item transport compression;
  \item surface compression.
\end{itemize}

Transport compression is presently represented only by the return-cell
transport. Surface compression is presently represented only by the six-nine
surface candidate.

This distinction remains descriptive. Nothing in the present work establishes
that every transport surface admits compression, that every surface rowset has
a compression interpretation, or that either class exhausts the possible
compression grammars of the G900 apparatus.

Likewise, the present results do not admit physical gravity. The term gravity
shadow remains project shorthand for a replay-stable grammar of registered
inward concentration.

The strongest present statement is therefore:

\begin{quote}
A local replay-stable bounded homeward-alignment compression signature exists
inside the G900 apparatus, and a distinct receipt-strong six-nine surface
candidate remains open.
\end{quote}

The next questions are naturally structural.

Can additional metric-ready transport surfaces be found?

Can a finite surface metric be defined for six-nine?

Can transport compression and surface compression be unified under a broader
finite compression grammar?

The current artifact sequence does not answer these questions. It establishes
only that they are now well-posed.
